Python to Assembly Compilation

### 2011-12-14 paper/paper.tex
fix label issue I introduced

\subsubsection{Temporary variables}
As a result of introducing the intermediate flattening stage, we introduce additional references to an object which hang around until the end of the given program scope.  This is undesirable because it changes the de-allocation behavior of the program from the expected behavior.  For original input program in figure~\ref{lst:simplebreak}, the expectation is that when the variable \texttt{a} is assigned the value zero, the reference count for the list object should be decremented to zero and the object de-allocated.  However, in the flattened program, this is no longer the case since the \texttt{tmp2} variable continues to reference the object.  The de-allocation is therefore delayed until the end of the current scope.  To handle this situation, we keep track of all temporary variables introduced as a result of flattening an expression.  These temporary variables are then assigned a value of zero immediately after the statement containing the expression in which they were introduced.  This will lead to an immediate decrement of the reference count after the reference counting AST transformation.  Figure~\ref{lst:fixflattened} shows the result of the flattening transformation after this change is made.

\begin{lstlisting}[
language=Python,
frame=topline,
caption={The flattened version of listing \ref{lst:simpleleak} with immediate de-allocation of temporary variables.},
captionpos=b,
label=lst:flattened
]
tmp0 = [1]
tmp1 = [2]
tmp2 = tmp0 + tmp1
a = tmp2
tmp2 = 0
tmp1 = 0
tmp0 = 0
a = 0
print a
\end{lstlisting}
\end{figure}

>>>>

\subsubsection{Temporary variables}
As a result of introducing the intermediate flattening stage, we introduce additional references to an object which hang around until the end of the given program scope.  This is undesirable because it changes the de-allocation behavior of the program from the expected behavior.  For original input program in figure~\ref{lst:simpleleak}, the expectation is that when the variable \texttt{a} is assigned the value zero, the reference count for the list object should be decremented to zero and the object de-allocated.  However, in the flattened program, this is no longer the case since the \texttt{tmp2} variable continues to reference the object.  The de-allocation is therefore delayed until the end of the current scope.  To handle this situation, we keep track of all temporary variables introduced as a result of flattening an expression.  These temporary variables are then assigned a value of zero immediately after the statement containing the expression in which they were introduced.  This will lead to an immediate decrement of the reference count after the reference counting AST transformation.  Figure~\ref{lst:fixflattened} shows the result of the flattening transformation after this change is made.

\begin{figure}[h!]
\begin{lstlisting}[
language=Python,
frame=topline,
caption={The flattened version of listing \ref{lst:simpleleak} with immediate de-allocation of temporary variables.},
captionpos=b,
label=lst:fixflattened
]
tmp0 = [1]
tmp1 = [2]
tmp2 = tmp0 + tmp1
a = tmp2
tmp2 = 0
tmp1 = 0
tmp0 = 0
a = 0
print a
\end{lstlisting}
\end{figure}
